Independent discovery of a nulling pulsar with unusual sub-pulse drifting properties with the Murchison Widefield Array

### 2022-04-05 paper/referee_report_1/response.md

8. It is difficult to determine whether nulling or just weak emission exists in this pulsar only from Figures 2 and 3. The pulse energy distribution is a statistical way to characterize the nulling behavior (Wen et al. 2020, ApJ, 904, 72).

  * We have now included pulse energy distributions for all six observations (see also our response to points 12 & 13 below). From the distributions of the two 20-min observations in which the pulsar was not detected in a periodicity search, we conclude that if there is any weak emission, it must fall far below the MWA's detection threshold. The new text discussing the pulse energy histograms can be found in Section 3.1.

9. Is there any temporal evolution of nulling fraction from follow-up observations and archival MWA data? Is it possible that the constraints on the nulling fraction might be reported in this paper?

  * It still remains the case that only a limited number of archival MWA data sets have been processed and analysed (being those which are presented in this paper). We do expect to get better constraints of the nulling fraction once more data have been processed, but this remains outside the scope of the present initial analysis, and will be presented in the planned follo-up paper.

### 2022-04-05 paper/referee_report_1/response.md

9. Is there any temporal evolution of nulling fraction from follow-up observations and archival MWA data? Is it possible that the constraints on the nulling fraction might be reported in this paper?

  * It still remains the case that only a limited number of archival MWA data sets have been processed and analysed (being those which are presented in this paper). We do expect to get better constraints of the nulling fraction once more data have been processed, but this remains outside the scope of the present initial analysis, and will be presented in the planned follo-up paper.

10. The nulls from a few pulsars does not seem to be random, but show well-defined periodicity (e.g. Herfindal & Rankin 2007, MNRAS, 380, 430; Wang et al. 2021, ApJ, 923, 259). Try to examine whether the periodicity in the transitions between null and burst states is present in this pulsar.

  * We have examined the fluctuation spectra for each of our data sets, but find no evidence of periodicity in the null-burst transitions. To be clear, the observations which showed any discernible low-frequency features at all were 1226062160, 1274143152 and 1283104232. For the latter two, the low-frequency feature occurred in the first (non-DC) frequency bin, which is not surprising, as this only reflects the fact that only one (long) nulling sequence was present in both. Similarly, the low-frequency feature in 1226062160's spectrum occurs in the second (non-DC) bin, corresponding to the presence of two main (long) null sequences. In all cases, the ratio of observation length to null length is too small to make any assertions about whether the observed null lengths are typical, or whether they are periodic or quasi-periodic. This will be explored in the future once more (and longer) follow-up observations have been made.

### 2022-04-06 paper/referee_report_1/response.md

9. Is there any temporal evolution of nulling fraction from follow-up observations and archival MWA data? Is it possible that the constraints on the nulling fraction might be reported in this paper?

  * It still remains the case that only a limited number of archival MWA data sets have been processed and analysed (being those which are presented in this paper). We do expect to get better constraints of the nulling fraction once more data have been processed, but this remains outside the scope of the present initial analysis, and will be presented in the planned follo-up paper.

10. The nulls from a few pulsars does not seem to be random, but show well-defined periodicity (e.g. Herfindal & Rankin 2007, MNRAS, 380, 430; Wang et al. 2021, ApJ, 923, 259). Try to examine whether the periodicity in the transitions between null and burst states is present in this pulsar.

  * We have examined the fluctuation spectra for each of our data sets, but find no evidence of periodicity in the null-burst transitions. To be clear, the observations which showed any discernible low-frequency features at all were 1226062160, 1274143152 and 1283104232. For the latter two, the low-frequency feature occurred in the first (non-DC) frequency bin, which is not surprising, as this only reflects the fact that only a single (long) nulling sequence was present in both. Similarly, the low-frequency feature in 1226062160's spectrum occurs in the second (non-DC) bin, corresponding to the presence of two main (long) null sequences. In all cases, the ratio of observation length to null length is too small to make any assertions about whether the observed null lengths are typical, or whether they are periodic or quasi-periodic. This will be explored in the future once more (and longer) follow-up observations have been made.

@@

11. The pulsar switches between null and burst states with short and long timescales, which provides an important clue to scrutinize various nulling mechanism models. The null and burst length histograms are required.

  * We completely agree that a deeper study of the state transitions has great potential to shed light on the nulling mechanism. However, at present, it is unclear how to treat

### 2022-04-27 paper/referee_report_1/response.md

10. The nulls from a few pulsars does not seem to be random, but show well-defined periodicity (e.g. Herfindal & Rankin 2007, MNRAS, 380, 430; Wang et al. 2021, ApJ, 923, 259). Try to examine whether the periodicity in the transitions between null and burst states is present in this pulsar.

  * We have examined the fluctuation spectra for each of our data sets, but find no evidence of periodicity in the null-burst transitions. To be clear, the observations which showed any discernible low-frequency features at all were 1226062160, 1274143152 and 1283104232. For the latter two, the low-frequency feature occurred in the first (non-DC) frequency bin, which is not surprising, as this only reflects the fact that only a single (long) nulling sequence was present in both. Similarly, the low-frequency feature in 1226062160's spectrum occurs in the second (non-DC) bin, corresponding to the presence of two main (long) null sequences. In all cases, the ratio of observation length to null length is too small to make any assertions about whether the observed null lengths are typical, or whether they are periodic or quasi-periodic. This will be explored in the future once more (and longer) follow-up observations have been made.

11. The pulsar switches between null and burst states with short and long timescales, which provides an important clue to scrutinize various nulling mechanism models. The null and burst length histograms are required.

  * We completely agree that a deeper study of the state transitions has great potential to shed light on the nulling mechanism. However, the working definition of nulls used in this work makes the suggested null and burst length analysis problematic, because no distinction is made between "true" nulls and pseudo-nulls. Consequently, long burst sequences that are likely continuous under a stricter definition of nulls are, in this analysis, frequently interrupted by (likely) pseudo-nulls (as can be clearly seen in the new Figure 2). This effectively alters the null and burst length histograms dramatically. Therefore, we feel that histograms of the null/burst lengths under the current definition would not contain as much useful information about the nulling mechanism as hoped. A deeper analysis is certainly required, but, we feel, outside the scope of the present paper.

### 2022-04-27 paper/main.tex
Finished a few more revisions for the referee

Each observation was individually calibrated using {\bf observations of 3C444 taken within $\sim 2$ hours of the respective target observations.
The calibration solutions were obtained using} the Real Time System software \citep{Mitchell2008}.
After calibration, the voltages were used to form a tied-array beam in the direction of the pulsar (the localization procedure is discussed in \S\ref{sec:localization}), using the bespoke beamforming software described in \citet{Ord2019}.
{\bf The MWA is located in a very radio quiet location, and no significant radio frequency interference was found in the beamformed data.}
After determining the best dispersion measure (DM) and period (see \S\ref{sec:period}), de-dispersion and folding were performed with {\tt DSPSR} \citep{VanStraten2011b} and {\tt PSRCHIVE} \citep{Hotan2004} to form single pulse archives, from which Stokes I pulse stacks were created.
Profiles of each detection, as well as an integrated profile incorporating the data from all four observations, is shown in Fig \ref{fig:profiles}.
Subsequent analysis of the pulse stacks is described in \S\ref{sec:analysis}.
\begin{figure}[!th]
    \centering
    \includegraphics[width=\linewidth]{profiles.png}
    \caption{{\bf Peak-normalised mean profiles of four of the observations}, and the total mean profile (top panel) including all four observations, with a time resolution of $\sim 1.3\,$ms. {\bf The two observations on MJD 59002 are not included here as they consist almost entirely of noise.} The profiles show a barely resolved double peak structure.}
    \label{fig:profiles}
\end{figure}

>>>>

Each observation was individually calibrated using {\bf observations of 3C444 taken within $\sim 2$ hours of the respective target observations.
The calibration solutions were obtained using} the Real Time System software \citep{Mitchell2008}.
After calibration, the voltages were used to form a tied-array beam in the direction of the pulsar (the localization procedure is discussed in \S\ref{sec:localization}), using the bespoke beamforming software described in \citet{Ord2019}.
{\bf The MWA is located in a very radio quiet location, and no significant radio frequency interference was found in the beamformed data.}
After determining the best dispersion measure (DM) and period (see \S\ref{sec:period}), de-dispersion and folding were performed with {\tt DSPSR} \citep{VanStraten2011b} and {\tt PSRCHIVE} \citep{Hotan2004} to form single pulse archives, from which Stokes I pulse stacks were created.
Profiles of each detection, as well as an integrated profile incorporating the data from all four observations, is shown in Fig \ref{fig:profiles}.
Subsequent analysis of the pulse stacks is described in \S\ref{sec:analysis}.
\begin{figure}[!th]
    \centering
    \includegraphics[width=\linewidth]{profiles.png}
    \caption{{\bf Peak-normalised mean profiles (black) of four of the observations}, and the total mean profile (top panel) including all four observations, with a time resolution of $\sim 1.3\,$ms. {\bf The two observations on MJD 59002 are not included here as they consist almost entirely of noise.} The profiles show a barely resolved double peak structure. {\bf The gray lines show the profiles made up only of pulses classified as nulls.}}
    \label{fig:profiles}
\end{figure}
